Practical Optional Types for Clojure

### 2015-02-21 overview.tex
add examples

>>>>

\inputminted[firstline=4]{clojure}{code/demo/src/demo/eg1.clj}
\inputminted[firstline=4]{clojure}{code/demo/src/demo/eg2.clj}
\inputminted[firstline=4]{clojure}{code/demo/src/demo/eg3.clj}
\inputminted[firstline=4]{clojure}{code/demo/src/demo/eg4.clj}
\inputminted[firstline=4,lastline=15]{clojure}{code/demo/src/demo/eg5.clj}
\inputminted[firstline=4,lastline=15]{clojure}{code/demo/src/demo/eg6.clj}
\inputminted[firstline=4,lastline=23]{clojure}{code/demo/src/demo/eg7.clj}
